---
title: "Keyword Impact Report"
subtitle: "Citations and Publications Insights"
institute: "School of Industrial Technology, Universiti Sains Malaysia"
pagetitle: "Keyword Impact Report | PPTI"
author: 
  - name: "Yusri Yusup, Wan Zafira Wan Zakaria, Lee Chee Keong, Norli Ismail, Abdorezza Mohammad Nafchi, Mohd Nurazzi Norizan, Melbi Mahardika"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: false
    df_print: paged
params:
  top_n: 25
  min_pubs_core: 10
  min_cites_core: 100
  csv_citations: "data/keyword_citation_counts.csv"
  csv_publications: "data/keyword_publication_count.csv"
  csv_journals: "data/keywords_journal_top.csv"
---

```{r params_fix, include=FALSE}
# If this Rmd is run outside Knit, params may not exist.
if (!exists("params")) {
  params <- list(
    top_n = 25,
    min_pubs_core = 10,
    min_cites_core = 100,
    csv_citations = "keyword_citation_counts.csv",
    csv_publications = "keyword_publication_count.csv",
    csv_journals = "keywords_journal_top.csv"
  )
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(dplyr)
library(readr)
library(stringr)
library(ggplot2)
library(scales)

# modern UI
#library(bslib)
library(DT)
library(plotly)
library(htmltools)

# ---------- helpers ----------
norm_key <- function(x) str_to_lower(str_squish(as.character(x)))

pick_col <- function(df, candidates) {
  nms <- names(df)
  nms_low <- str_to_lower(nms)
  idx <- match(str_to_lower(candidates), nms_low, nomatch = 0)
  if (all(idx == 0)) return(NA_character_)
  nms[idx[idx != 0][1]]
}

safe_read_csv <- function(path) read_csv(path, show_col_types = FALSE, progress = FALSE)

# ----- Theme (Bootstrap 5) -----
#bs_theme_set(
#  bs_theme(
#    version = 5,
#    bootswatch = "flatly",
#    base_font = font_google("Inter"),
#    heading_font = font_google("Inter")
#  )
#)


```
<style>
.hero {
  padding: 18px 18px;
  border-radius: 18px;
  background: rgba(255,255,255,.9);
  border: 1px solid rgba(0,0,0,.06);
  box-shadow: 0 10px 30px rgba(0,0,0,.08);
  border: 1px solid rgba(0,0,0,.06);
  margin-bottom: 18px;
}

.subtitle {
  color: #111827 !important;   /* charcoal / near-black */
}

.kpi-grid{
  display:grid;
  grid-template-columns: repeat(4, minmax(0, 1fr));
  gap: 12px;
  margin: 14px 0 22px 0;
}
.stat-card{
  position: relative;
  border-radius: 18px;
  background: #ffffff;
  box-shadow: 0 10px 30px rgba(0,0,0,.08);
  border-top: 6px solid #111827;
  overflow: hidden;
}

.stat-card .card-body{
  padding: 16px 18px;
}

.card-title{
  color:#6b7280;
  font-weight:700;
  font-size:13px;
  text-transform:uppercase;
  letter-spacing:.08em;
}

.stat-value{
  font-size:34px;
  font-weight:900;
}
.kpi .label{ font-size: .85rem; color:#6c757d; }
.kpi .value{ font-size: 1.35rem; font-weight: 800; margin-top: 4px; }
.kpi .hint{ font-size: .80rem; color:#6c757d; margin-top: 4px; }

@media (max-width: 992px){
  .kpi-grid{ grid-template-columns: repeat(2, minmax(0, 1fr)); }
}
@media (max-width: 576px){
  .kpi-grid{ grid-template-columns: repeat(1, minmax(0, 1fr)); }
}

/* Typography */
h2 { margin-top: 1.3rem; font-weight: 900; letter-spacing: -0.2px; }
h3 { margin-top: 1rem; font-weight: 800; color: #0b5ed7; letter-spacing: -0.15px; }
p  { line-height: 1.55; }

/* Section card wrapper */
.section{
  border-radius: 18px;
  padding: 18px 20px;
  background: #ffffff;
  box-shadow: 0 10px 30px rgba(0,0,0,.08);
  border: none;
}

/* Small note text */
.note {
  color:#6c757d;
  font-size: .92rem;
  margin-top: -6px;
  margin-bottom: 10px;
}

/* DT table polish */
table.dataTable {
  border-radius: 14px !important;
  overflow: hidden;
}
.dataTables_wrapper .dataTables_filter input {
  border-radius: 999px !important;
  padding: 6px 10px !important;
  border: 1px solid rgba(0,0,0,.15) !important;
}
.dataTables_wrapper .dataTables_paginate .paginate_button {
  border-radius: 10px !important;
}
.dataTables_wrapper .dataTables_info {
  color: #6c757d !important;
}

/* Plotly chart container */
.plotly {
  border-radius: 18px;
  border: 1px solid rgba(0,0,0,.06);
  box-shadow: 0 10px 30px rgba(0,0,0,.06);
  padding: 6px;
  background: #fff;
}

/* Smooth scroll */
html { scroll-behavior: smooth; }

/* Floating back button */
#backTop {
  position: fixed;
  bottom: 22px;
  right: 22px;
  z-index: 9999;
  background: #0b5ed7;
  color: #fff;
  border-radius: 999px;
  padding: 10px 14px;
  font-size: 0.85rem;
  font-weight: 600;
  box-shadow: 0 8px 20px rgba(0,0,0,.2);
  text-decoration: none;
}
#backTop:hover { background: #084298; }
</style>



```{r}
cit_raw <- safe_read_csv(params$csv_citations)
pub_raw <- safe_read_csv(params$csv_publications)
jr_raw  <- safe_read_csv(params$csv_journals)

# --- detect columns ---
cit_kw_col  <- pick_col(cit_raw, c("Keyword","keyword","Keywords","Term"))
cit_val_col <- pick_col(cit_raw, c("Total Citations","Citations","citation_count","total_citations"))

pub_kw_col  <- pick_col(pub_raw, c("Keyword","keyword","Keywords","Term"))
pub_val_col <- pick_col(pub_raw, c("Publication Count","Publications","pub_count","count","publication_count"))

jr_kw_col   <- pick_col(jr_raw,  c("Keywords","Keyword","keyword","Term"))
jr_j_col    <- pick_col(jr_raw,  c("Journal","Source","journal"))
jr_c_col    <- pick_col(jr_raw,  c("Count","count","N","n"))

stopifnot(!is.na(cit_kw_col), !is.na(cit_val_col))
stopifnot(!is.na(pub_kw_col), !is.na(pub_val_col))
stopifnot(!is.na(jr_kw_col),  !is.na(jr_j_col), !is.na(jr_c_col))

cit <- cit_raw %>%
  transmute(keyword = norm_key(.data[[cit_kw_col]]),
            citations = suppressWarnings(as.numeric(.data[[cit_val_col]]))) %>%
  group_by(keyword) %>% summarise(citations = sum(citations, na.rm=TRUE), .groups="drop") %>%
  filter(!is.na(keyword), keyword != "")

pub <- pub_raw %>%
  transmute(keyword = norm_key(.data[[pub_kw_col]]),
            pubs = suppressWarnings(as.numeric(.data[[pub_val_col]]))) %>%
  group_by(keyword) %>% summarise(pubs = sum(pubs, na.rm=TRUE), .groups="drop") %>%
  filter(!is.na(keyword), keyword != "")

jr <- jr_raw %>%
  transmute(keyword = norm_key(.data[[jr_kw_col]]),
            journal  = as.character(.data[[jr_j_col]]),
            count    = suppressWarnings(as.numeric(.data[[jr_c_col]]))) %>%
  group_by(keyword, journal) %>%
  summarise(count = sum(count, na.rm=TRUE), .groups="drop") %>%
  filter(!is.na(keyword), keyword != "", !is.na(journal), journal != "")

```

```{r}
kw <- full_join(cit, pub, by="keyword") %>%
  mutate(
    citations = coalesce(citations, 0),
    pubs      = coalesce(pubs, 0),
    cit_per_pub = if_else(pubs > 0, citations / pubs, NA_real_),
    impact_score = citations * log1p(pubs)
  )

n_keywords <- nrow(kw)
total_cit  <- sum(kw$citations, na.rm=TRUE)
total_pub  <- sum(kw$pubs, na.rm=TRUE)

core <- kw %>%
  filter(pubs >= params$min_pubs_core, citations >= params$min_cites_core) %>%
  arrange(desc(citations), desc(pubs))

```
**Prepared by:** Research Trends Committee 2025, School of Industrial Technology, Universiti Sains Malaysia.

# Executive Summary
This report presents a structured overview of research keywords associated with publications produced by the School of Industrial Technology (PPTI), with the aim of supporting strategic research planning and publication decision-making. By examining keyword usage alongside citation influence and journal associations, the analysis identifies established thematic strengths, emerging areas of high potential, and patterns of journal alignment relevant to PPTI’s research portfolio. The findings provide an evidence-based foundation for refining research focus, guiding manuscript preparation, and strengthening the alignment between research outputs and appropriate publication outlets. This report is intended to serve as a living reference that can be updated periodically to reflect evolving research directions and scholarly impact within the school.


```{r}
#core <- kw %>%
#  filter(pubs >= params$min_pubs_core, citations >= params$min_cites_core) %>%
#  arrange(desc(citations), desc(pubs))

#core_tbl <- core %>%
#  transmute(
#    keyword,
#    citations = fmt_int(citations),
#    publications = fmt_int(pubs),
#    citations_per_pub = fmt_num(cit_per_pub, 2),
#    impact_score = fmt_num(impact_score, 2)
#  )

# KPI cards
```{r}
kpi <- tags$div(class = "row",

  tags$div(class = "col-sm-3",
    tags$div(class = "card stat-card",
      tags$div(class = "card-body",
        tags$div(class = "card-title", "Total keywords"),
        tags$div(class = "stat-value", comma(n_keywords)),
        tags$div(class = "note", "Unique keyword entries after cleaning")
      )
    )
  ),

  tags$div(class = "col-sm-3",
    tags$div(class = "card stat-card",
      tags$div(class = "card-body",
        tags$div(class = "card-title", "Total citations"),
        tags$div(class = "stat-value", comma(total_cit)),
        tags$div(class = "note", "Sum of keyword citations")
      )
    )
  ),

  tags$div(class = "col-sm-3",
    tags$div(class = "card stat-card",
      tags$div(class = "card-body",
        tags$div(class = "card-title", "Total publications"),
        tags$div(class = "stat-value", comma(total_pub)),
        tags$div(class = "note", "Sum of keyword publication counts")
      )
    )
  ),

  tags$div(class = "col-sm-3",
    tags$div(class = "card stat-card",
      tags$div(class = "card-body",
        tags$div(class = "card-title", "Core keywords"),
        tags$div(class = "stat-value", comma(nrow(core))),
        tags$div(
          class = "note",
          paste0("pubs >= ", params$min_pubs_core,
                 " & cites >= ", params$min_cites_core)
        )
      )
    )
  )

)

htmltools::HTML(as.character(kpi))


```


```{r}
top_journals <- jr %>%
  arrange(keyword, desc(count)) %>%
  group_by(keyword) %>%
  slice_head(n = 3) %>%
  summarise(top_journals = paste0(journal, " (", count, ")", collapse="; "),
            .groups="drop")

core_view <- core %>%
  left_join(top_journals, by="keyword") %>%
  transmute(
    keyword,
    citations = citations,
    publications = pubs,
    citations_per_pub = round(cit_per_pub, 2),
    impact_score = round(impact_score, 2),
    top_journals = coalesce(top_journals, "-")
  )
```

# Core Keywords (High Citations and Publications)
Keywords that demonstrate strong combined performance in both citation impact and publication volume.



```{r}
DT::datatable(
  core_view,
  rownames = FALSE,
  options = list(
    pageLength = 10,
    autoWidth = FALSE,
    scrollX = TRUE
  )
) %>%
  DT::formatCurrency(c("citations","publications"), currency = "", interval = 3) %>%
  DT::formatRound(c("citations_per_pub","impact_score"), digits = 2)


```


```{r}
top_cited <- kw %>% arrange(desc(citations)) %>% slice_head(n = params$top_n)

p1 <- ggplot(
  top_cited %>% mutate(keyword = reorder(keyword, citations)),
  aes(
    x = keyword, y = citations,
    fill = citations,
    text = paste0(
      "<b>", keyword, "</b><br>",
      "Citations: ", comma(citations), "<br>",
      "Publications: ", comma(pubs), "<br>",
      "Citations/pub: ", round(cit_per_pub, 2), "<br>",
      "Impact score: ", round(impact_score, 2)
    )
  )
) +
  geom_col(width = 0.85) +
  coord_flip() +
  scale_fill_gradient(low = "#e5e7eb", high = "#111827") +
  labs(
    title = paste0("Top ", params$top_n, " Keywords by Citations"),
    x = NULL, y = "Total citations", fill = "Citations"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.major.y = element_blank(),
    legend.position = "none"
  )

```

# Top Keywords by Citations
Interactive bar chart (hover to see details).

```{r}
plotly::ggplotly(p1, tooltip = "text") %>%
  layout(margin = list(l = 40, r = 20, t = 60, b = 30))


```

# Top Keywords by Citations
Detailed statistics for keywords shown in the citations chart.

```{r}
DT::datatable(
  top_cited %>%
    transmute(
      keyword,
      citations,
      publications = pubs,
      citations_per_pub = round(cit_per_pub, 2),
      impact_score = round(impact_score, 2)
    ),
  rownames = FALSE,
  options = list(
    pageLength = 10,
    autoWidth = FALSE,
    scrollX = TRUE
  )
) %>%
  DT::formatCurrency(c("citations","publications"), currency="", interval=3)


```


```{r}
top_pubs <- kw %>% arrange(desc(pubs)) %>% slice_head(n = params$top_n)

p2 <- ggplot(
  top_pubs %>% mutate(keyword = reorder(keyword, pubs)),
  aes(
    x = keyword, y = pubs,
    fill = pubs,
    text = paste0(
      "<b>", keyword, "</b><br>",
      "Publications: ", comma(pubs), "<br>",
      "Citations: ", comma(citations), "<br>",
      "Citations/pub: ", round(cit_per_pub, 2), "<br>",
      "Impact score: ", round(impact_score, 2)
    )
  )
) +
  geom_col(width = 0.85) +
  coord_flip() +
  scale_fill_gradient(low = "#e5e7eb", high = "#111827") +
  labs(
    title = paste0("Top ", params$top_n, " Keywords by Publications"),
    x = NULL, y = "Publication count", fill = "Publications"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.major.y = element_blank(),
    legend.position = "none"
  )


```
# Top Keywords by Publications
Interactive bar chart (hover to see details).
```{r}
plotly::ggplotly(p2, tooltip = "text") %>%
  layout(margin = list(l = 40, r = 20, t = 60, b = 30))

```

# Top Keywords by Publications
Keywords ranked by number of publications

```{r jr_overall_build}
jr_overall <- jr %>%
  group_by(journal) %>%
  summarise(total_keyword_mentions = sum(count, na.rm=TRUE), .groups="drop") %>%
  arrange(desc(total_keyword_mentions)) %>%
  slice_head(n = params$top_n)
```

```{r}
DT::datatable(
  top_pubs %>%
    transmute(
      keyword,
      publications = pubs,
      citations,
      citations_per_pub = round(cit_per_pub, 2),
      impact_score = round(impact_score, 2)
    ),
  rownames = FALSE,
  options = list(
    pageLength = 10,
    autoWidth = FALSE,
    scrollX = TRUE
  )
) %>%
  DT::formatCurrency(c("citations","publications"), currency="", interval=3)


```
# Emerging High-Impact Keywords
Keywords with high citation impact per publication but relatively low publication volume.

```{r}
# choose high-citation but low-output keywords
emerging <- kw %>%
  filter(pubs > 0, pubs <= 3, citations > 0) %>%
  arrange(desc(cit_per_pub), desc(citations)) %>%
  slice_head(n = params$top_n)
```



```{r}
DT::datatable(
  emerging %>%
    transmute(
      keyword,
      citations,
      publications = pubs,
      citations_per_pub = round(cit_per_pub, 2)
    ),
  rownames = FALSE,
  options = list(
    pageLength = 10,
    autoWidth = FALSE,
    scrollX = TRUE
  )
)%>%
  DT::formatCurrency(c("citations","publications"), currency="", interval=3)


```

# Journals with Highest Keyword Frequency
Journals most frequently associated with high-impact keywords.

```{r}
jr_overall <- jr %>%
  group_by(journal) %>%
  summarise(total_keyword_mentions = sum(count, na.rm=TRUE), .groups="drop") %>%
  arrange(desc(total_keyword_mentions)) %>%
  slice_head(n = params$top_n)
```


```{r}
DT::datatable(
  jr_overall,
  rownames = FALSE,
  options = list(
    pageLength = 10,
    autoWidth = FALSE,
    scrollX = TRUE
  )
) %>%
  DT::formatCurrency("total_keyword_mentions", currency="", interval=3)



```

